### 2017-10-29 paper.tex
CoC

Finally,
working in the open can be great,
but can also unintentionally suppress voices.
Programming Historian makes an ombudsperson available for private chats and facilitation
to ensure that no one is excluded.

>>>>

Finally,
working in the open can be great,
but can also unintentionally suppress voices.
Programming Historian makes an ombudsperson available for private chats and facilitation
to ensure that no one is excluded.
Software Carpentry operates by a Code of Conduct that outlines acceptable standards of behavior for our community members
and those interacting with the Carpentries at in-person events and in virtual spaces.
Community members on a Policy Subcommittee serve as advocates for the Code of Conduct
and adjudicate reported violations.
